The emotion--facial expression link: Evidence from human and automatic expression recognition

### 2020-08-28 manuscript/manuscript_apa.Rmd
review

The confusion matrices obtained by crossing encoders’ self-reports, human annotations and the automatic recognition are analysed by calulating two-sided Pearson correlation, accuracy which corresponds to the overall agreement rate averaged over cross-validation iterations and Cohen’s (unweighted) Kappa.

>>>>

The confusion matrices obtained by crossing encoders’ self-reports, human annotations and the automatic recognition are analysed by calculating two-sided Pearson correlation, accuracy which corresponds to the overall agreement rate averaged over cross-validation iterations and Cohen’s (unweighted) Kappa.

### 2020-08-28 revision/prpf_1/revision_letter.Rmd
review

@@

@@

>>>>

```{r setup, include = FALSE}
# libraries --------------------------------------------------------------------
library(tidyverse)
library(magrittr)
library(here)
library(ltm)

# options ----------------------------------------------------------------------
set.seed(123)
options(scipen = 999)
knitr::opts_chunk$set(
  cache.extra = knitr::rand_seed,
  cache = FALSE,
  message = FALSE, 
  warning = FALSE, 
  error = FALSE, 
  echo = FALSE
  )

# data -------------------------------------------------------------------------

## self_report_data
source(here::here("script/data_wrangling_self_report.R"))
self_report_score <- self_report_score %>%
  dplyr::select(C_Video, sr_emotion = emotion, sr_score = value)

## human_recognition_data
source(here::here("script/data_wrangling_human_recognition.R"))
human_recognition_score <- human_recognition_score %>%
  dplyr::select(C_Video, hr_emotion = emotion, hr_score = confidence_score)

## automatic_recognition_data
source(here::here("script/data_wrangling_automatic_recognition.R"))
automatic_recognition_score <- automatic_recognition_score %>%
  dplyr::select(C_Video, ar_emotion = emotion, ar_score = confidence_score) %>%
  dplyr::filter(C_Video %in% ppt_per_video$C_Video)

list_video <- human_recognition_score$C_Video
list_emotion <- c("disgust","fear","happiness","surprise","sadness","anger")

grid_data <- expand.grid(list_video = list_video, list_emotion = list_emotion)

self_report_result <- self_report_score %>%
  dplyr::filter(sr_emotion != "undetermined") %>%
  dplyr::mutate(sr_score = 1)

human_recognition_result <- human_recognition_score %>%
  dplyr::filter(hr_emotion != "undetermined") %>%
  dplyr::mutate(hr_score = 1)

automatic_recognition_result <- automatic_recognition_score %>%
  dplyr::filter(ar_emotion != "undetermined") %>%
  dplyr::mutate(ar_score = 1)

recognition_result <- grid_data %>%
  dplyr::left_join(
    self_report_result,
    by = c(
      "list_video" = "C_Video",
      "list_emotion" = "sr_emotion"
      )
    ) %>%
  dplyr::left_join(
    human_recognition_result,
    by = c(
      "list_video" = "C_Video",
      "list_emotion" = "hr_emotion"
      )
    ) %>%
  dplyr::left_join(
    automatic_recognition_result,
    by = c(
      "list_video" = "C_Video",
      "list_emotion" = "ar_emotion"
      )
    ) %>%
  replace(is.na(.), 0)
```

@@

We greatly appreciate the Reviewer’s positive comments. We have carefully revised the manuscript according to the Reviewer’s insightful comments and provided point-by-point responses as follows.

@@

```{r echo=TRUE}
recognition_result %$%
  ltm::biserial.cor(sr_score, hr_score, level = 2)

recognition_result %$%
  cor.test(sr_score, hr_score, method = "pearson", alternative = "two.sided") %>% 
  use_series("estimate")
```
